\section{Conclusion and Future work}
\label{conclusion}
In this paper, we have introduced the Byzantine Reliable Broadcast problem on partially connected networks and fully connected networks where the topology is known to all processes. We started by introducing the current state of the problem and how the original protocols work. We continued by elaborating on how one can find the required paths through the network for Dolev, and then how this information can be used to build routing tables for processes. We then described \textbf{9} modifications to Dolev, Bracha, and Bracha-Dolev, and evaluated each modification separately. When we combine all modifications, we provide a solution with a lower message complexity and network usage than existing solutions, a reduction of 71.9\% and 79.4\% respectively with a 12B payload when $N=150$ and $f=20$ for Dolev.
We have concluded that we can indeed reduce the number of messages transmitted when processes have topology knowledge.

This work can be extended in the future by deploying our modified protocols on real infrastructure to get accurate measurements as opposed to simulations. Furthermore, the disjoint path solver can likely be further optimized by enhancing the pathfinding and (re)using better-suited data structures. Applying our modifications to dynamic networks should also be researched further. In addition to this, we use several simple heuristics in our paper (\textbf{ORB.2}, \textbf{ORD.5}) which should be replaced by optimal solutions or improved heuristics. Another interesting direction is that of topology discovery~\cite{topology-discovery,explorer,explorer2}. Previously unknown networks can use optimizations specific for known networks when matched with a topology discovered. One challenge to overcome in this scenario is the tolerance for imperfect routing tables.

%It might also be interesting to explore the combination of our modifications and (multi-)signatures to further reduce the number of messages transmitted.
